Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
table mis indexing
table figures
rename a file

\begin{table*}
\centering
\begin{tabular}{|l|l|l|l|}
\hline 
\textbf{Example} & \textbf{Target} & \textbf{Simulation} & \textbf{Printed Result}\\
\hline 
Texture&  \includegraphics[width=3cm]{figure/globeTarget.png}& \includegraphics[width=3cm]{figure/globeSim.png}
& \includegraphics[width=3cm]{figure/globe.png}\\
&  \includegraphics[width=3cm]{figure/mapTarget.png}& \includegraphics[width=3cm]{figure/mapSim.png}
& \includegraphics[width=3cm]{figure/map.png}\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:example}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{llll}  %error metric is not interesting
\hline 
\textbf{Example} & \textbf{Reducer Nodes} & \textbf{Simulator} & \textbf{Optimization}\\
\hline 
Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
Caustics 1 & Column, QuadLayerMaterial & & SA \\
Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
\hline
\end{tabular}
\caption{Fabricated results.}
\label{tab:result}
\end{table*}

>>>>

\begin{table*}
\centering
\begin{tabular}{llll}  %error metric is not interesting
\hline 
\textbf{Example} & \textbf{Reducer Nodes} & \textbf{Simulator} & \textbf{Optimization}\\
\hline 
Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
Caustics 1 & Column, QuadLayerMaterial & & SA \\
Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
\hline
\end{tabular}
\caption{Fabricated results.}
\label{tab:example}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{|p{2cm}|l|l|l|}
\hline 
\textbf{Example} & \textbf{Target} & \textbf{Simulation} & \textbf{Printed Result}\\
\hline 
Texture&  \includegraphics[width=3cm]{figure/globeTarget.png}& \includegraphics[width=3cm]{figure/globeSim.png}
& \includegraphics[width=3cm]{figure/globe.png}\\
&  \includegraphics[width=3cm]{figure/mapTarget.png}& \includegraphics[width=3cm]{figure/mapSim.png}
& \includegraphics[width=3cm]{figure/map.png}\\
\hline
Subsurface Scattering&  \includegraphics[width=3cm]{figure/chessTarget.png}& \includegraphics[width=3cm]{figure/chessSim.png}
& \includegraphics[width=3cm]{figure/chess.png}\\
\hline
Caustics &  \includegraphics[width=3cm]{figure/causticsTarget.png}& \includegraphics[width=3cm]{figure/causticsSim.png}
& \includegraphics[width=3cm]{figure/caustics.png}\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:result}
\end{table*}
